Analysis of the included studies

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Removed thesis path and commented out prisma chart code

#save figures in this folder
save_fig_here <- '../figs_manuscript'

save_thesis_fig_here <- "C:/Users/JAMESAZAM/Dropbox/My Academic Repository/_SACEMA/Academic/_PhD/__PhD_Thesis/_Thesis_LaTeX/figs/chapter_3"
```

```{r}
# Load the cleaned data 
long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')

#a vector of shorter replacements for the original parametrization descriptions
parametrization_str_replacements <- c('values_from_literature' = 'literature', 
                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
                  'values_fitted_to_ts' = 'fitted',
                  ' ' = ' and ' #replace space with 'and' to make it more readable
                  )

#a vector of shorter replacements for the original validation descriptions
validation_str_replacements <- c('compared_with_data' = 'data',
                                 'compared_with_other_model_output' = 'another_model',
                                 'model_not_validated' = 'none',
                                 ' ' = '_and_'
                                 )

# The data with citations 
compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))

@@

```{r eval=FALSE}
library(PRISMAstatement)

prisma_chart <- prisma(found = 12986,
       found_other = 0,
       no_dupes = 5012, 
       extra_dupes_box = TRUE,
       screened = 5012, 
       screen_exclusions = 4211, 
       full_text = 801,
       full_text_exclusions = 548, 
       qualitative = 253, 
       quantitative = 0,
       width = 800, height = 800,
       font_size = 12)

prisma_chart
```

>>>>

#save figures in this folder
save_fig_here <- '../figs_manuscript'
```

```{r}
# Load the cleaned data 
long_data <- read_rds('../data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
```

```{r}
# Dictionary of parametrization methods descriptions
parametrization_dict <- c('values_from_literature' = 'literature', 
                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
                  'values_fitted_to_ts' = 'fitted',
                  ' ' = ' and ' #replace space with 'and' to make it more readable
                  )

# Dictionary of validation methods descriptions
validation_dict <- c('compared_with_data' = 'data',
                                 'compared_with_other_model_output' = 'another_model',
                                 'model_not_validated' = 'none',
                                 ' ' = '_and_'
                                 )

# The data with citations 
compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')

@@

<!-- # ```{r eval=FALSE} -->
<!-- # library(PRISMAstatement) -->
<!-- #  -->
<!-- # prisma_chart <- prisma(found = 12986, -->
<!-- #        found_other = 0, -->
<!-- #        no_dupes = 5012,  -->
<!-- #        extra_dupes_box = TRUE, -->
<!-- #        screened = 5012,  -->
<!-- #        screen_exclusions = 4211,  -->
<!-- #        full_text = 801, -->
<!-- #        full_text_exclusions = 548,  -->
<!-- #        qualitative = 253,  -->
<!-- #        quantitative = 0, -->
<!-- #        width = 800, height = 800, -->
<!-- #        font_size = 12) -->
<!-- #  -->
<!-- # prisma_chart -->
<!-- # ``` -->
